% Statement.tex
%==============================================================================
\section{Thesis Statement and Research Objectives}
\label{sec:statement}
%==============================================================================

%-- Problem
\noindent 

%==============================================================================
\subsection{Thesis Statement}
\label{subsec:statement}
%==============================================================================

Develop a runtime system to execute integration processes for business intelligence in the context of cloud computing.

%==============================================================================
\subsection{Primary Objective of Research}
\label{subsec:primary_objectives}
%==============================================================================

Reduce the average processing time of a message through the integration process, considering concurrently the optimization of the computational resources - threads and memory - needed in this process.

%==============================================================================
\subsection{Secondary Research Objectives}
\label{subsec:secondary_objectives}
%==============================================================================

\begin{itemize}
\item Minimize thread management time, in relation to the creation, destruction and context change of them.
\item Minimize the waiting time of a task in the ready queues.
\item Minimize task processing time.
\item Maximizing the total amount of messages processed by the integration process per time unit.
\item Minimizing the time gap between a task becomes ready to execute and its execution completion.
\item Avoid thread concentration in the initial tasks of the integration flow in the task queue when there is an increase in the incoming message load.
\end{itemize}